An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
almost finished

Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory and the Borda Technology for the indoor dataset retrieval.

>>>>

Authors would like to thank for the collaboration and the equipments to ITU Robotics Laboratory, and Borda Technology for the indoor dataset retrieval.
